Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-26 paper/ijcai/paper.tex
eating up some space
paper
spell checking

		\bottomrule
	\end{tabular}
	\caption {Dynamic Slicing performance on capturing faulty statements, as
     percentages. Higher is better.}
   \label{tab:ds-cases-captured}
\vspace{-0.2cm}

@@

Table \ref{table:st} presents the statistics to determine if the
observed results are statistically significant. Shapiro-Wilk tests the
null hypothesis that results are drawn from a normal distribution. The
test is perfomed for all techniques and values of $k$. With $99\%$
confidence, the results tell us that the distributions are not
normal. Given that $C$ is not normally distributed, we used Friedman, a
non-parametric statistical test of hypothesis. The null hypothesis is
that the rankings obtained with all techniques and variants are the
same. With $99\%$ confidence, the results show that the distributions
are distinct. To understand which techniques perform differently,
\ie{}, to answer the question \textit{Does \combpar{k} perform
  differently than \sfl{}$^{k}$}, we performed a Siegel post-hoc
analysis. Figure \ref{fig:performance} reports results. Each square
shows the statistical significance of the difference in diagnostic
accuracy amongst the different techniques--the lighter color and
smaller value of $p$ indicates higher significance. Based on these
results, it is possible to determine with $95\%$ confidence that the
performance of each pair of techniques is different.

\begin{figure}[h]
	\vspace{-1cm}
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Siegel post-hoc analysis results}
		\label{fig:performance}
		\vspace{-0.3cm}
\end{figure}

As the results are statistically significant, it is possible to state
that \combpar{k} has a positive effect on the localization of some
types of bugs. There is indeed a problem on using slicing on fault of
omission bugs that needs further research.  Although, this dataset has
more than $50\%$ of fault of omissions, our simple slicing approach
was capable of improving the ranking of $95$ faults for $k=5$ and
$115$ faults for $k=10$. These may be promissing results from what Automated
Program Repair (APR) techniques may directly benefit to improve the accuracy
of their own techniques.

\subsection{Threats to validity}
%
A potential threat to \textit{external validity} relates to the set of programs used in
our study. When choosing the projects for our study, our aim was to opt for
projects that resemble a general and large-sized application. To reduce
selection bias and facilitate the comparison of our results, we decided to
choose a benchmark that is popular in the community~\cite{just-defects4j-issta2014}.
Our study did not evaluate the faults from the \closure{}
project because of the high CPU cost of running \combpar{k} on it. A potential
threat to \textit{construct validity} relates to the choice of oracle
we used for the Lithium slicer. We found empirically that our choice was able to capture 
the faults for the cases we analyzed.
The main threat to \textit{internal validity} lies in the complexity of several of the tools
used in our experiments, most notably the Lithium toolset, the SFL diagnosis tool,
and the implementation of \comb{}. To mitigate this threat, we
carefully inspected our code and looked for discrepancies and
incoherences in our results.

@@

Prior work has investigated the \ds{}-\sfl{}
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}.
Overall, these studies reported promissing results but based their conclusions
on a very small group of (mostly artificial) faults and using different
techniques. In this
study, a larger set of faults is evaluated and a more rigorous experimental
methodology.
In contrast with other studies on this combination,
our approach is the first using Critical Slicing to minimize test cases
and leveraging \sfl{} rank to choose and minimize the top-$k$ of
highest-ranked faulty classes.

@@

Despite tacit opinions of the research community about the usefulness
of \ds~in automated debugging, we found te \ds{}-\sfl{} combination
practical (as per the relatively low number of misses) and effective
(as per the improvements of $\Delta(C)$ on the relevant cases), and
encourage new \sfl~techniques to be evaluated against that
optimization.  Future work includes 1)~improving our oracle heuristics
to handle more exceptions, 2)~conducting experiments in more \dfj{}
faults and other datasets, and 3)~handling cases of faults of
omission.

@@

%%  LocalWords:  SFL

>>>>

		\bottomrule
	\end{tabular}
	\caption {Dynamic Slicing performance on capturing faulty statements, as
     percentages. Higher is better.}
   \label{tab:ds-cases-captured}

@@

Table \ref{table:st} presents the statistics to determine if the
observed results are statistically significant. Shapiro-Wilk tests the
null hypothesis that results are drawn from a normal distribution. The
test is performed for all techniques and values of $k$. With $99\%$
confidence, the results tell us that the distributions are not
normal. Given that $C$ is not normally distributed, we used Friedman, a
non-parametric statistical test of hypothesis. The null hypothesis is
that the rankings obtained with all techniques and variants are the
same. With $99\%$ confidence, the results show that the distributions
are distinct. To understand which techniques perform differently,
\ie{}, to answer the question \textit{Does \combpar{k} perform
  differently than \sfl{}$^{k}$}, we performed a Siegel post-hoc
analysis. Figure \ref{fig:performance} reports results. Each square
shows the statistical significance of the difference in diagnostic
accuracy amongst the different techniques--the lighter color and
smaller value of $p$ indicates higher significance. Based on these
results, it is possible to determine with $95\%$ confidence that the
performance of each pair of techniques is different.

\begin{figure}[h]
	\vspace{-1cm}
		\includegraphics[width=0.48\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Siegel post-hoc analysis results}
		\label{fig:performance}
		\vspace{-0.3cm}
\end{figure}

As the results are statistically significant, it is possible to state
that \combpar{k} has a positive effect on the localization of some
types of bugs. There is indeed a problem on using slicing on fault of
omission bugs that needs further research.  Although, this dataset has
more than $50\%$ of fault of omissions, our simple slicing approach
was capable of improving the ranking of $95$ faults for $k=5$ and
$115$ faults for $k=10$. These may be promising results from what Automated
Program Repair (APR) techniques may directly benefit to improve the accuracy
of their own techniques.

\subsection{Threats to validity}
%
A potential threat to \textit{external validity} relates to the set of programs used in
our study. When choosing the projects for our study, our aim was to opt for
projects that resemble a general and large-sized application. To reduce
selection bias and facilitate the comparison of our results, we decided to
choose a benchmark that is popular in the community~\cite{just-defects4j-issta2014}.
Our study did not evaluate the faults from the \closure{}
project because of the high CPU cost of running \combpar{k} on it. A potential
threat to \textit{construct validity} relates to the choice of oracle
we used for the Lithium slicer. We found empirically that our choice was able to capture 
the faults for the cases we analyzed.
The main threat to \textit{internal validity} lies in the complexity of several of the tools
used in our experiments, most notably the Lithium toolset, the SFL diagnosis tool,
and the implementation of \comb{}. To mitigate this threat, we
carefully inspected our code and looked for discrepancies and
incoherence in our results.

@@

Prior work has investigated the \ds{}-\sfl{}
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}.
Overall, these studies reported promising results but based their conclusions
on a very small group of (mostly artificial) faults and using different
techniques. In this
study, a larger set of faults is evaluated and a more rigorous experimental
methodology.
In contrast with other studies on this combination,
our approach is the first using Critical Slicing to minimize test cases
and leveraging \sfl{} rank to choose and minimize the top-$k$ of
highest-ranked faulty classes.

@@

Despite tacit opinions of the research community about the usefulness
of \ds~in automated debugging, we found the \ds{}-\sfl{} combination
practical (as per the relatively low number of misses) and effective
(as per the improvements of $\Delta(C)$ on the relevant cases), and
encourage new \sfl~techniques to be evaluated against that
optimization.  Future work includes 1)~improving our oracle heuristics
to handle more exceptions, 2)~conducting experiments in more \dfj{}
faults and other datasets, and 3)~handling cases of faults of
omission.

@@

%%  LocalWords:  SFL dataset suspiciousness MBSD DS DX anonymized NPE
%%  LocalWords:  ij pq Ochiai ochiai significative Siegel hoc amongst
%%  LocalWords:  toolset scalability
